Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-13 july18meeting_pres2/may30ccgmeeting.tex
Updates

	\section{Differential Expression}
	\begin{frame}{Finding Differentially Expressed Genes}
		\begin{itemize}
			\item Reads are count based hence they cannot be normally distributed
		\end{itemize}
	\end{frame}

>>>>

	\section{Differential Expression}
	%Our data do not fit the Poisson distribution
	%(i.e. Poisson will underestimate variability leading to an increase in false positive DE genes).
	\begin{frame}{Why does DESeq2 Use the Negative Binomial Distribution}
		\begin{itemize}
			\item Reads are count based hence they cannot be normally distributed
			\item Variance tends to be greater than the mean, especially for genes with large mean expression values
			\item  We need to account for this increase in variance using the Negative Binomial model 
		\end{itemize}
	\centering \includegraphics[width=5.5cm, height=5.5cm]{all_cancersmean_vs_variance_male.png}
	\end{frame}

	\begin{frame}{DESeq2 Accounts for Increased Variance}
		\begin{enumerate}
			\item Estimate gene-wise dispersions: captures biological variability in gene expression across samples
			\item Fit negative binomial GLM to count data: This model incorporates the estimated gene-wise dispersions as a parameter to account for variability in the data
			\item Use fitted GLM to identify differentially expressed genes \newline
		\end{enumerate}
		The use of linear models allows for more complex designs \newline \newline
		$design = ~cancertype + condition$ \newline \newline
		This tells DESeq2 to test the effect of condition while controlling for the effect of cancer type
	\end{frame}

	\begin{frame}{Finding Differentially Expressed Genes (DESeq2)}
